\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-07 psharp.tex
update

We have implemented multiple schedulers inside the \psharp runtime: \emph{random}, \emph{depth-first-search (DFS)}, ..., \emph{PCT}. It is easy to create a new scheduler by implementing the \texttt{ISchedulingStrategy} interface exposed by the \psharp libraries. The interface exposes callbacks that are invoked by the \psharp runtime for taking decisions regarding which machine to schedule next, and can be used for developing both generic and application-specific schedulers, although we have experimented only with generic schedulers so far. Exposing an intuitive interface for creating new schedulers is inspired by previous work~\cite{desai2015tr}.

>>>>

We have implemented two schedulers inside the \psharp runtime: \emph{random}, and \emph{probabilistic concurrency testing} (PCT)~\cite{burckhardt2010pct}. It is straightforward to create a new scheduler by implementing the \texttt{ISchedulingStrategy} interface exposed by the \psharp libraries. The interface exposes callbacks that are invoked by the \psharp runtime for taking decisions regarding which machine to schedule next, and can be used for developing both generic and application-specific schedulers, although we have experimented only with generic schedulers so far. Exposing an easy-to-use interface for creating new schedulers is inspired by previous work~\cite{desai2015tr}.
